Efficient pedigree recording for fast population genetics simulation

### 2017-12-30 forwards_paper.tex
Add note about consistent term for two implementations

To demonstrate the method's flexibility and to test it in different contexts,
we implemented these simulations separately using two different simulation engines:
\begin{enumerate}

    \item
        In \cpp{}, using \fwdpp{} library functions and interface code (details below),
        using a continuum-sites model for both mutation and recombination. Simulations were run using \fwdpy{}, a Python
        package based on \fwdpp.
        % $\mu$ and $r$ were the means of Poisson processes,
        % and mutations used the infinite-sites model \citep{Kimura1969-uc}.
        % We varied $N \in (1000, 10000, 50000)$, $\rho \in (10^3, 10^4, 10^5)$.

>>>>

To demonstrate the method's flexibility and to test it in different contexts,
we implemented these simulations separately using two different simulation engines:

\jda{Note/TODO: the varying references to c++, python, fwdpp, fwdpy11 and
	simupop are probably confusing to a new reader. This is in part because
	we refer to the python/simupop method in various places as one or the
	other; the same goes for c++/fwdpy11/fwdpp. We should decide what to
	call these and make our usage consistent}

\begin{enumerate}

    \item
        In \cpp{}, using \fwdpp{} library functions and interface code (details below),
        using a continuum-sites model for both mutation and recombination. Simulations were run using \fwdpy{}, a Python
        package based on \fwdpp.
        % $\mu$ and $r$ were the means of Poisson processes, and mutations used the infinite-sites model \citep{Kimura1969-uc}.
        % We varied $N \in (1000, 10000, 50000)$, $\rho \in (10^3, 10^4, 10^5)$.
